---
title: "GAEZ Localized Drainage Class"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
#set libary path
required.packages <- c("sf", "readr", "dplyr", "tidyr", "purrr", "reticulate", "Rcpp", "stringr", "utils", "httr", "jsonlite", "here", "raster", "aqp", "GSIF","XML", "rgdal","gdalUtils", "viridis", "rasterVis")
new.packages <- required.packages[!(required.packages %in% installed.packages()[, 
    "Package"])]
if (length(new.packages)) install.packages(new.packages)
lapply(required.packages, require, character.only = T)
rm(required.packages, new.packages)

```


# Site-based soil drainage class
1. Calculate all soil types mapped in Ghana based on WISE
2. Subset GAEZ Soil Drainage Characteristics table
3. Evaluate variation in classification based on soil type and phases, e.g., vertic, gelic, and root limiting layers.
4. Create generalized lookup table based on phase criteria we can gather from LandPKS soil limitations, texture, slope
```{r}
ssa_countries <- read_sf('C:/R_Drive/Data_Files/LPKS_Data/R_Projects/LPKS.Ghana/data/raw_data/Countries.shp')
ghana <- ssa_countries %>% dplyr::filter(COUNTRY=='Ghana')
#WISE30sec
wise_spatial <- read_sf("C:/LandPKS_API_SoilID-master/global/wise30sec_poly_simp_soil.shp")
wise_spatial <- st_make_valid(wise_spatial)
wise_ghana <- intersect(as_Spatial(wise_spatial), as_Spatial(ghana))
wise <- read.csv("C:/LandPKS_API_SoilID-master/global/wise_full_soil.csv")
wise_gh_data <- wise %>% dplyr::filter(MU_GLOBAL %in% wise_ghana$MU_GLOBAL)

#list of unique taxonomy in Ghana
gh_tax <- unique(wise_gh_data$CLAF)
# Import existing GAEZ Soil Drainage Characteristics table
GAEZ_Soil_Drainage <- read.csv('C:/R_Drive/Data_Files/LPKS_Data/Projects/Ghana/Data/GAEZ/soil_drainage_requirements_FAO_90.csv')

gh_drainage_req <- GAEZ_Soil_Drainage %>% dplyr::filter(FAO90_CODE %in% gh_tax)

gh_drainage_req_long <- gh_drainage_req %>% pivot_longer(!c(FAO90_CODE, T_TEXTURE), names_to = "require", values_to = "class")
gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(Phase = case_when(grepl("NP", require) ~ "PH0",
                            grepl("PH1", require) ~"PH1",
                            grepl("PH2", require) ~"PH2"))
gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(Slope = case_when(
                            grepl("0.0p5", require) ~ "0_p5",
                            grepl("0p5.2", require) ~ "p5_2",
                            grepl("2.5", require) ~ "2_5",
                            grepl("S5.10", require) ~ "5_10",
                            grepl("10.15", require) ~ "10_15",
                            grepl("15.30", require) ~ "15_30",
                            grepl("30.45", require) ~ "30_45",
                            grepl("S45_100", require) ~"45_100"))

gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(saturation = case_when(
                            grepl("g", FAO90_CODE, ignore.case = FALSE) ~ "saturation",
                            grepl("j", FAO90_CODE, ignore.case = FALSE) ~ "saturation",
                            grepl("PL", FAO90_CODE, ignore.case = FALSE) ~ "saturation",
                            grepl("GL", FAO90_CODE, ignore.case = FALSE) ~ "saturation",
                            grepl("PT", FAO90_CODE, ignore.case = FALSE) ~ "saturation",
                            grepl("p", FAO90_CODE, ignore.case = FALSE) ~ "saturation",
                            grepl("PH2", Phase, ignore.case = FALSE) ~ "saturation"))

gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(shallow = case_when(
                            grepl("LP", FAO90_CODE, ignore.case = FALSE) ~ "shallow"))

gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(hardpan = case_when(
                            grepl("PT", FAO90_CODE, ignore.case = FALSE) ~ "hardpan",
                            grepl("p", FAO90_CODE, ignore.case = FALSE) ~ "hardpan",
                            grepl("PH1", Phase, ignore.case = FALSE) ~ "hardpan"))
gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(vertic = case_when(                            
                            grepl("VR", FAO90_CODE, ignore.case = FALSE) ~ "vertic"))
gh_drainage_req_long <- gh_drainage_req_long %>% dplyr::mutate(histic = case_when(
                            grepl("HS", FAO90_CODE, ignore.case = FALSE) ~ "histosol"))
                            


View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5")) #Restr_Grp=='G2' & 
#phases: PH1=Petroferric/Duripan/ Placic/Lithic phases; PH2=Anthraquic phase
#1. Shallow = c('LP', )
#2a. Saturation = c('g', 'j','PL', 'GL')
#2b. Root restriction = c('PT', 'p')
#2c. Vertic = c('VR')
#3. Histosols = 'HS'

```

# Manual Review of restriction ratings
Approach:
1. Set texture class,  
2. set slope class, and 
3. evaluate restrictions for each texture/slope combination


```{r}
#All restriction combinations for texture=1 and slope 0-0.5
# View histic
View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5" & !is.na(histic)))
# View vertic
View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5" & !is.na(vertic)))
# View saturation
View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5" & !is.na(saturation) & is.na(vertic) & is.na(histic)))
# View hardpan restriction
View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5" & !is.na(hardpan) & is.na(saturation)& is.na(shallow) & is.na(vertic)& is.na(histic)))
# View shallow
View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5" & !is.na(shallow)))
# View no restrictions
View(gh_drainage_req_long %>% dplyr::filter(T_TEXTURE==1 & Slope=="0_p5" & is.na(hardpan) & is.na(saturation)& is.na(shallow) & is.na(vertic)& is.na(histic)))


# Based on manual filtering of the data, I created a generalized table of rating criteria for deriving drainage class. In the future
# this could be automated by sumarizing the count of each drainage class within each criteria and taking the max class. Gleysols and Fluvosols 
# are outlier soils based on the current rating criteria. Need to put some more thought into how to deal with these. 
# Changed 'Texture' column name to 'PSCL_ID'
# Load in generalized rating criteria table for generating site-based soil drainage classes.
drainage_class_reqs <- read.csv('C:/R_Drive/Data_Files/LPKS_Data/Projects/Ghana/Data/GAEZ/soil_drainage_class_requirements_RF_low.csv')
```


# Function to calculate drainage class

Need to filter based on these restrictions:
1. Histic = currently no LPKS input, default to (Histic = 'No')
2. Saturation = flooding (flooding = 'Frequent')
3. Vertic = cracks (cracks = 'Yes') & texture group = F
4. Hardpan = is_compaction_layer (is_compaction_layer = 'Yes')
5. Shallow = bedrock_depth (bedrock_depth <=50)
6. No restriction

LPKS inputs: texture, slope, flooding, cracks, is_compaction_layer, bedrock_depth
```{r}
drainage_class_calc <-  function(drainage_class_reqs, texture, slope, flooding, cracks, PSCL, is_compaction_layer, bedrock_depth){
  histic=='No'
  if(flooding == 'Frequent'){
    Saturation == 'Yes' 
  } else {
    Saturation == 'No' 
  }
  if(PSCL=='F' & cracks == 'Yes'){
    Vertic=='Yes'
  } else {
    Vertic=='No'
  }
  if(is_compaction_layer == 'Yes'){
    Hardpan =='Yes'
  } else {
    Hardpan == 'No'
  }
  if(bedrock_depth <=50){
    Shallow == 'Yes'
  } else {
    Shallow == 'No'
  }
  
}


  
  
  
  
  
```
