---
title: "GAEZ Downscaling Ghana"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
#set libary path
required.packages <- c("sf", "readr", "dplyr", "tidyr", "purrr", "reticulate", "Rcpp", "stringr", "utils", "httr", "jsonlite", "here", "raster", "aqp", "GSIF","XML", "rgdal","gdalUtils", "viridis", "rasterVis", "ggplot2", "foreach")
new.packages <- required.packages[!(required.packages %in% installed.packages()[, 
    "Package"])]
if (length(new.packages)>0){ install.packages(new.packages)}
lapply(required.packages, require, character.only = TRUE)
rm(required.packages, new.packages)

```

# Validation Data
```{r}
Validation_Soil_Data <- read.csv('C:/R_Drive/Data_Files/LPKS_Data/Projects/Ghana/Project Documents/Field_Sampling/Field_Data/Validation_Data/CSIR_LPKS_Validation_Soil_Data2021-04-16.csv')

Validation_Site_Data <- read.csv('C:/R_Drive/Data_Files/LPKS_Data/Projects/Ghana/Project Documents/Field_Sampling/Field_Data/Validation_Data/CSIR_LPKS_Validation_Site_Data2021-04-16.csv')

Validation_Lab_Data  <- read.csv('C:/R_Drive/Data_Files/LPKS_Data/Projects/Ghana/Project Documents/Field_Sampling/Field_Data/Validation_Data/Validation_Lab_Data.csv')



Validation_Soil_Data <- Validation_Soil_Data %>% full_join(Validation_Lab_Data, by=c('CSIR_Pit', 'bottom')) %>% left_join(Validation_Site_Data %>% dplyr::select(CSIR_Pit, slope, soilDepth, waterTableDepth, flooding, stoniness, is_compaction_layer), by=c('CSIR_Pit'))

```

# EPA data from validation sites
```{r}
#load in processed LandPKS Cocoa data sites
EPA_Site_Data <- readRDS('C:/R_Drive/Data_Files/LPKS_Data/R_Projects/LPKS.Ghana/data/private_data/Ghana_LPKS_Site_Data.rds')
EPA_Soil_Data <- readRDS('C:/R_Drive/Data_Files/LPKS_Data/R_Projects/LPKS.Ghana/data/private_data/Ghana_LPKS_Soil_Data.rds')
EPA_Soil_Data <- EPA_Soil_Data %>% dplyr::select(id, name, bedrock_depth, cracks, bottom, texture, rfv_class, soil_color, latitude, longitude) %>% dplyr::mutate(bedrock_depth = as.integer(bedrock_depth))
EPA_Soil_Data <- EPA_Soil_Data %>% dplyr::filter(name %in% Validation_Soil_Data$name)
EPA_Soil_Data <- EPA_Soil_Data %>% dplyr::rename(Pedon_ID = id) %>% dplyr::mutate(bedrock_depth = bedrock_depth %>% as.numeric() %>% tidyr::replace_na(NaN))
EPA_Soil_Data <- EPA_Soil_Data  %>% left_join(EPA_Site_Data %>% dplyr::select(name, slope, flooding, stoniness, is_compaction_layer, surface_salt, waterTableDepth, soilDepth), by='name') %>% distinct()


#join Pedon_ID to Validation_Soil_Data
Validation_Soil_Data <- Validation_Soil_Data %>% left_join(EPA_Soil_Data %>% dplyr::select(name, Pedon_ID), by='name') %>% distinct() %>% dplyr::filter(bottom<=70) %>% dplyr::mutate(bedrock_depth = bedrock_depth %>% as.numeric() %>% tidyr::replace_na(NaN))

```

# CEC clay calculation for validation sites
```{r}

S_Class <- function(rating){
  if(rating >= 95){
    SC <- 'S0'
  } else if(rating < 95 & rating >= 85){
    SC <- 'S1'
  } else if(rating < 85 & rating >= 60){
    SC <- 'S2'
  } else if(rating < 60 & rating >= 40){
    SC <- 'S3'
  } else if(rating < 40 & rating >= 10){
    SC <- 'S4'
  } else if(rating < 10){
    SC <- 'N'
  } 
  return(SC)
}

getClay <- function(texture){
        if(is.na(texture) | texture==""){
          clay <- NA
        }else{
            txt_l <- stringr::str_to_lower(texture)
            if(txt_l == "sand"){
                clay <- 5.0
            }else if(txt_l == "loamy sand"){
                clay <- 7.5
            }else if(txt_l == "sandy loam"){
                clay <- 10.0
            }else if(txt_l == "sandy clay loam"){
                clay <- 27.5
            }else if(txt_l == "loam"){
                clay <- 17.0
            }else if(txt_l == "silt"){
                clay <- 6.0
            }else if(txt_l == "silt loam"){
                clay <- 13.5
            }else if(txt_l == "silty clay loam"){
                clay <- 33.5
            }else if( txt_l == "clay loam"){
                clay <- 33.5
            }else if(txt_l == "sandy clay"){
                clay <- 45.0
            }else if(txt_l == "silty clay"){
                clay <- 50.0
            }else if(txt_l == "clay"){
                clay <- 70.0
            }}
        return(clay)
}
Validation_Soil_Data <- Validation_Soil_Data %>% rowwise() %>% dplyr::mutate(clay = getClay(texture)) %>% ungroup()
Validation_Soil_Data <- Validation_Soil_Data %>% rowwise() %>% dplyr::mutate(CECc = (ECEC - (250*(OC*.001)))/(clay/100))
Validation_Soil_Data <- Validation_Soil_Data %>% rowwise() %>% dplyr::mutate(ESP = ((Na/(Na+Ca+Mg+K))*100))
#CECs <- (prof$CECS - (250*(prof$ORGC*.001)))/(prof$CLPC/100)
```


# FarmGrow data
```{r}
LPKS_FG_Data <- readRDS(here('data/derived_data/LPKS_FG_Data.rds'))
LPKS_FG_Data_val <- LPKS_FG_Data %>% dplyr::filter(name %in% Validation_Soil_Data$name) 

```

# Compile data for comparison
```{r}
Validation_Sites_Compare <- Validation_Soil_Data %>% dplyr::select(name,CSIR_Pit, Pedon_ID, bottom, texture, rfv_class,OC, OM, pH, N, P_mgkg, K) %>% dplyr::filter(bottom == 1) %>% left_join(LPKS_FG_Data_val %>% dplyr::select(name, Productivity, Recommendation, Genetics,Farm.Condition,Farm.age,Tree.health, Weeding, Pruning, Tree.age, Tree.density, Harvesting, Pest.Sanitation, Shade.Management), by="name")


Val_site_tax <- data.frame(c("P1", "P2", "P3",  "P4",  "P5",  "P6",  "P7",  "P8",  "P9", "P10"), c("Ferric Lixisol", 'Haplic Acrisol', "Ferric Lixisol",'Ferric Acrisol', 'Haplic Lixisol', 'Ferric Acrisol', 'Ferric Acrisol','Haplic Lixisol','Haplic Lixisol','Haplic Lixisol'), c('Swedru', 'Nzima', 'Swedru', 'Bekwai', 'Kokofu', 'Bekwai', 'Bekwai', 'Kokofu', 'Eshiem', 'Kokofu')) %>% purrr::set_names('CSIR_Pit', "WRB", "series")

Validation_Sites_Compare <- Validation_Sites_Compare %>% left_join(Val_site_tax, by="CSIR_Pit")
Validation_Soil_Data <- Validation_Soil_Data %>% left_join(Val_site_tax, by="CSIR_Pit")
```


# EPA pedon data
```{r}
pedon_test_list <- unique(EPA_Soil_Data$Pedon_ID)
GH.profiles.epa <- list(list())

#Progress combine function
n <- length(pedon_test_list)
pb <- txtProgressBar(min = 1, max = n, style=3)

stime <- system.time({ 
GH.profiles.epa <- foreach(i= 1:length(pedon_test_list), .packages = c("stringr", "dplyr", "tidyr", "XML", "reticulate", "purrr", "jsonlite")) %do% {
  setTxtProgressBar(pb, i)
  tryCatch({
      pedon <- EPA_Soil_Data %>% dplyr::filter(Pedon_ID==pedon_test_list[i])
      pedon$texture <- pedon$texture %>% replace_na("")
      pedon$rfv_class <- pedon$rfv_class %>% replace_na("")
      if (length(as.character(pedon$texture))>1) {
        soilHorizon=as.character(pedon$texture)
      } else {
        soilHorizon=list(as.character(pedon$texture))
      }
      if (length(pedon$rfv_class)>1) {
        rfvDepth=pedon$rfv_class
      } else {
        rfvDepth=list(pedon$rfv_class)
      }
      if (length(as.integer(pedon$bottom))>1) {
        horizonDepth=as.integer(pedon$bottom)
      } else {
        horizonDepth=list(as.integer(pedon$bottom))
      }
      lon=as.numeric(unique(pedon$longitude))
      lat=as.numeric(unique(pedon$latitude))
      if (is.na(as.numeric(unique(pedon$bedrock_depth)))){
        bedrock = NULL
      } else {
        bedrock = as.numeric(unique(pedon$bedrock_depth))
      }
      plot_id <- unique(pedon$Pedon_ID)
      # lab_Color <- list(list())
      # for(j in 1:nrow(pedon)){
      #   lab_Color[j] <- list(c(pedon$D.L[j], pedon$D.a[j], pedon$D.b[j]))
      # }
      # base.url.list1 <-"http://127.0.0.1:5000/api/v1/soilidlist?"
      # base.url.rank1 <-"http://127.0.0.1:5000/api/v1/soilidrank?"
      base.url.list2 <-"http://127.0.0.1:5000/api/v2/soilidlist?"
      base.url.rank2 <-"http://127.0.0.1:5000/api/v2/soilidrank?"
      depth.text <- ""
      for(j in 1:length(horizonDepth)){
        depth <- paste0("&soilHorizon", j, "_Depth=", horizonDepth[j])
        if(str_detect(toupper(soilHorizon[j]), " ")==TRUE){
            text <- paste0("&soilHorizon", j, "=", str_replace_all(toupper(soilHorizon[j]), " ", "%20"))
        } else {
          text <- paste0("&soilHorizon", j, "=", toupper(soilHorizon[j]))
        }
        RFV <- paste0("&soilHorizon", j, "_RFV=", rfvDepth[j])
        depth.text <- paste0(depth.text, depth, text, RFV)
      }
      # depth.color <- ""
      # for(j in 1:length(lab_Color)){
      #   color <- paste0("&soilHorizon", j, "_LAB=", paste0(lab_Color[[j]], collapse =","))
      #   depth.color <- paste0(depth.color, color)
      # }
      # url.list1 <- paste0(base.url.list1, "longitude=", lon, "&latitude=", lat)
      # url.rank1 <- paste0(base.url.rank1, "longitude=", lon, "&latitude=", lat, depth.text, "&cracks=False")#,"&slope=",pSlope, depth.color)
      url.list2 <- paste0(base.url.list2, "longitude=", lon, "&latitude=", lat, "&plot_id=", plot_id)
      url.rank2 <- paste0(base.url.rank2, "longitude=", lon, "&latitude=", lat, depth.text, "&cracks=False&plot_id=", plot_id)#,"&slope=",pSlope, depth.color)
      querry_time <- system.time({
      # result_list1 <- possibly(fromJSON, "Failed")(url.list1, simplifyDataFrame =TRUE)  
      # result_out1 <- possibly(fromJSON, "Failed")(url.rank1, simplifyDataFrame = TRUE)
      result_list2 <- possibly(fromJSON, "Failed")(url.list2, simplifyDataFrame =TRUE)  
      result_out2 <- possibly(fromJSON, "Failed")(url.rank2, simplifyDataFrame = TRUE)
      })[3]
      SoilID_compID <-  result_out2$soilRank %>% dplyr::filter(rank_data==1) %>% dplyr::select(componentID) %>% set_names('SoilID_compID')
      Dom_compID <-  result_out2$soilRank %>% dplyr::filter(rank_loc==1) %>% dplyr::select(componentID) %>% set_names('Dom_compID')
      Pedon_id <- data.frame(unique(pedon$Pedon_ID)) %>% set_names('Pedon_ID')
      GH.profiles.epa[[i]] <- cbind(Pedon_id,Dom_compID,SoilID_compID)
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
close(pb)
})[3]
stime

GH.profiles.epa.df <- bind_rows(GH.profiles.epa)

```


# validation pedon data
```{r}
pedon_test_list <- unique(Validation_Soil_Data$Pedon_ID)
GH.profiles.val <- list(list())

#Progress combine function
n <- length(pedon_test_list)
pb <- txtProgressBar(min = 1, max = n, style=3)

stime <- system.time({ 
GH.profiles.val <- foreach(i= 1:length(pedon_test_list), .packages = c("stringr", "dplyr", "tidyr", "XML", "reticulate", "purrr", "jsonlite")) %do% {
  setTxtProgressBar(pb, i)
  tryCatch({
      pedon <- Validation_Soil_Data %>% dplyr::filter(Pedon_ID==pedon_test_list[i])
      pedon$texture <- pedon$texture %>% replace_na("")
      pedon$rfv_class <- pedon$rfv_class %>% replace_na("")
      if (length(as.character(pedon$texture))>1) {
        soilHorizon=as.character(pedon$texture)
      } else {
        soilHorizon=list(as.character(pedon$texture))
      }
      if (length(pedon$rfv_class)>1) {
        rfvDepth=pedon$rfv_class
      } else {
        rfvDepth=list(pedon$rfv_class)
      }
      if (length(as.integer(pedon$bottom))>1) {
        horizonDepth=as.integer(pedon$bottom)
      } else {
        horizonDepth=list(as.integer(pedon$bottom))
      }
      lon=as.numeric(unique(pedon$longitude))
      lat=as.numeric(unique(pedon$latitude))
      if (is.na(as.numeric(unique(pedon$bedrock_depth)))){
        bedrock = NULL
      } else {
        bedrock = as.numeric(unique(pedon$bedrock_depth))
      }
      plot_id <- unique(pedon$Pedon_ID)
      # lab_Color <- list(list())
      # for(j in 1:nrow(pedon)){
      #   lab_Color[j] <- list(c(pedon$D.L[j], pedon$D.a[j], pedon$D.b[j]))
      # }
      # base.url.list1 <-"http://127.0.0.1:5000/api/v1/soilidlist?"
      # base.url.rank1 <-"http://127.0.0.1:5000/api/v1/soilidrank?"
      base.url.list2 <-"http://127.0.0.1:5000/api/v2/soilidlist?"
      base.url.rank2 <-"http://127.0.0.1:5000/api/v2/soilidrank?"
      depth.text <- ""
      for(j in 1:length(horizonDepth)){
        depth <- paste0("&soilHorizon", j, "_Depth=", horizonDepth[j])
        if(str_detect(toupper(soilHorizon[j]), " ")==TRUE){
            text <- paste0("&soilHorizon", j, "=", str_replace_all(toupper(soilHorizon[j]), " ", "%20"))
        } else {
          text <- paste0("&soilHorizon", j, "=", toupper(soilHorizon[j]))
        }
        RFV <- paste0("&soilHorizon", j, "_RFV=", rfvDepth[j])
        depth.text <- paste0(depth.text, depth, text, RFV)
      }
      # depth.color <- ""
      # for(j in 1:length(lab_Color)){
      #   color <- paste0("&soilHorizon", j, "_LAB=", paste0(lab_Color[[j]], collapse =","))
      #   depth.color <- paste0(depth.color, color)
      # }
      # url.list1 <- paste0(base.url.list1, "longitude=", lon, "&latitude=", lat)
      # url.rank1 <- paste0(base.url.rank1, "longitude=", lon, "&latitude=", lat, depth.text, "&cracks=False")#,"&slope=",pSlope, depth.color)
      url.list2 <- paste0(base.url.list2, "longitude=", lon, "&latitude=", lat, "&plot_id=", plot_id)
      url.rank2 <- paste0(base.url.rank2, "longitude=", lon, "&latitude=", lat, depth.text, "&cracks=False&plot_id=", plot_id)#,"&slope=",pSlope, depth.color)
      querry_time <- system.time({
      # result_list1 <- possibly(fromJSON, "Failed")(url.list1, simplifyDataFrame =TRUE)  
      # result_out1 <- possibly(fromJSON, "Failed")(url.rank1, simplifyDataFrame = TRUE)
      result_list2 <- possibly(fromJSON, "Failed")(url.list2, simplifyDataFrame =TRUE)  
      result_out2 <- possibly(fromJSON, "Failed")(url.rank2, simplifyDataFrame = TRUE)
      })[3]
      SoilID_compID <-  result_out2$soilRank %>% dplyr::filter(rank_data==1) %>% dplyr::select(componentID) %>% set_names('SoilID_compID')
      Dom_compID <-  result_out2$soilRank %>% dplyr::filter(rank_loc==1) %>% dplyr::select(componentID) %>% set_names('Dom_compID')
      Pedon_id <- data.frame(unique(pedon$Pedon_ID)) %>% set_names('Pedon_ID')
      GH.profiles.val[[i]] <- cbind(Pedon_id,Dom_compID,SoilID_compID)
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
close(pb)
})[3]
stime

GH.profiles.val.df <- bind_rows(GH.profiles.val)

```


# Run GAEZ SQ on validation sites for Cocoa
```{r}
# Ghana cocoa Low level rain-fed
library(reticulate)
use_python("C:/Users/jmaynard/anaconda3/python.exe")
reticulate::source_python("C:/LandPKS_API_SoilID-master/model/GAEZ_soilID_functions_lab-data.py")

SQI_dom_L <- list(list())
SQI_id_L <- list(list())
SQI_id_loc_L_epa <- list(list())
SQI_id_loc_L_val <- list(list())
SQI_id_loc_L_val_lab <- list(list())

for(i in 1:nrow(GH.profiles.val.df)){
  pedon_epa <- EPA_Soil_Data %>% dplyr::filter(Pedon_ID==GH.profiles.val.df$Pedon_ID[i])
  pedon_val <- Validation_Soil_Data %>% dplyr::filter(Pedon_ID==GH.profiles.val.df$Pedon_ID[i])
  SQI_dom_L[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$Dom_compID, CROP_ID='49a', inputLevel='L', depthWt_type=2)
  SQI_id_L[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='49a', inputLevel='L', depthWt_type=2)
  SQI_id_loc_L_epa[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='49a', inputLevel='L', depthWt_type=2, plot_data=pedon_epa, site_data=pedon_epa)
  SQI_id_loc_L_val[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='49a', inputLevel='L', depthWt_type=2, plot_data=pedon_val, site_data=pedon_val)
  SQI_id_loc_L_val_lab[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='49a', inputLevel='L', depthWt_type=2, plot_data=pedon_val, site_data=pedon_val, lab_data=pedon_val)
}


SQI_dom_L_df <-  bind_rows(SQI_dom_L)
SQI_dom_L_df <-  SQI_dom_L_df %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_dom=SQ1, SQ2_dom=SQ2, SQ3_dom=SQ3, SQ4_dom=SQ4, SQ5_dom=SQ5, SQ6_dom=SQ6, SQ7_dom=SQ7, SR_dom=SR, Input_Level = `Input Level`, SoilTax_dom=`Soil Tax`)

SQI_id_L_df <-  bind_rows(SQI_id_L)
SQI_id_L_df <-  SQI_id_L_df %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id=SQ1, SQ2_id=SQ2, SQ3_id=SQ3, SQ4_id=SQ4, SQ5_id=SQ5, SQ6_id=SQ6, SQ7_id=SQ7, SR_id=SR, Input_Level = `Input Level`, SoilTax_id=`Soil Tax`)

SQI_id_loc_L_df_epa <-  bind_rows(SQI_id_loc_L_epa)
SQI_id_loc_L_df_epa <-  SQI_id_loc_L_df_epa %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id_loc_epa=SQ1, SQ2_id_loc_epa=SQ2, SQ3_id_loc_epa=SQ3, SQ4_id_loc_epa=SQ4, SQ5_id_loc_epa=SQ5, SQ6_id_loc_epa=SQ6, SQ7_id_loc_epa=SQ7, SR_id_loc_epa=SR, Input_Level = `Input Level`, SoilTax_id_loc_epa=`Soil Tax`)

SQI_id_loc_L_df_val <-  bind_rows(SQI_id_loc_L_val)
SQI_id_loc_L_df_val <-  SQI_id_loc_L_df_val %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id_loc=SQ1, SQ2_id_loc=SQ2, SQ3_id_loc=SQ3, SQ4_id_loc=SQ4, SQ5_id_loc=SQ5, SQ6_id_loc=SQ6, SQ7_id_loc=SQ7, SR_id_loc=SR, Input_Level = `Input Level`, SoilTax_id_loc=`Soil Tax`)

SQI_id_loc_L_df_val_lab <-  bind_rows(SQI_id_loc_L_val_lab)
SQI_id_loc_L_df_val_lab <-  SQI_id_loc_L_df_val_lab %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id_loc_lab=SQ1, SQ2_id_loc_lab=SQ2, SQ3_id_loc_lab=SQ3, SQ4_id_loc_lab=SQ4, SQ5_id_loc_lab=SQ5, SQ6_id_loc_lab=SQ6, SQ7_id_loc_lab=SQ7, SR_id_loc_lab=SR, Input_Level = `Input Level`, SoilTax_id_loc_lab=`Soil Tax`)

LandPKS_SQI_L <- SQI_dom_L_df %>% full_join(SQI_id_loc_L_df_epa, by=c('PedonID', 'Input_Level')) %>% full_join(SQI_id_loc_L_df_val, by=c('PedonID', 'Input_Level')) %>% full_join(SQI_id_loc_L_df_val_lab, by=c('PedonID', 'Input_Level')) %>% dplyr::select(PedonID,Input_Level, SoilTax_dom, SoilTax_id_loc_epa, SoilTax_id_loc, SoilTax_id_loc_lab, SQ1_dom, SQ1_id_loc_epa, SQ1_id_loc, SQ1_id_loc_lab, SQ2_dom, SQ2_id_loc_epa, SQ2_id_loc, SQ2_id_loc_lab, SQ3_dom, SQ3_id_loc_epa, SQ3_id_loc, SQ3_id_loc_lab, SQ4_dom, SQ4_id_loc_epa, SQ4_id_loc, SQ4_id_loc_lab, SQ5_dom, SQ5_id_loc_epa, SQ5_id_loc, SQ5_id_loc_lab, SQ6_dom, SQ6_id_loc_epa, SQ6_id_loc, SQ6_id_loc_lab, SQ7_dom, SQ7_id_loc_epa, SQ7_id_loc, SQ7_id_loc_lab, SR_dom, SR_id_loc_epa, SR_id_loc, SR_id_loc_lab)


Ghana_aez <- LandPKS_SQI_L %>% dplyr::select(id=PedonID, Input_Level, SR_dom, SR_id_loc_epa, SR_id_loc, SR_id_loc_lab) %>% pivot_longer(cols=SR_dom:SR_id_loc_lab, names_to = 'source', values_to='SR')

Ghana_aez$source <- factor(Ghana_aez$source, levels = c('SR_dom', 'SR_id_loc_epa', 'SR_id_loc', 'SR_id_loc_lab'))

Ghana_aez %>% dplyr::group_by(source) %>% dplyr::summarize(mean(SR, na.rm=T), sd(SR, na.rm=T))
Ghana_aez_sub <- Ghana_aez %>% dplyr::filter(!source=='SR_id')

Ghana_aez_sub <- Ghana_aez_sub %>% rowwise() %>% dplyr::mutate(SC = S_Class(SR))
Ghana_aez_sub$SC <- factor(Ghana_aez_sub$SC, order = TRUE, levels =  c( "S0", "S1", "S2", "S3", "S4", "N"))


# Draw the basic boxplot
pdf(here("results/figures/Ghana_AEZ_boxplot_cocoa.pdf"), width = 6.5, height = 4.5)
a <- boxplot(Ghana_aez$SR ~ Ghana_aez$source , ylim=c(0,100), ylab="Soil Suitability" , xlab="Data Source" ,main="Cocoa Soil Suitability")
dev.off()

col_bl <- c("#4575b4","#91bfdb", "#e0f3f8", "#fee090", "#fc8d59", "#d73027")
agg <- count(Ghana_aez_sub %>% dplyr::group_by(source), SC)  
pdf(here("results/figures/Ghana_AEZ_barplot_cocoa.pdf"), width = 6.5, height = 4.5)
  ggplot(agg) +
      geom_col(aes(x = source, y = n, fill = SC)) +
      scale_fill_manual(values = col_bl)
  
dev.off() 

```


# Run GAEZ SQ on validation sites for Maize
```{r}
# Ghana maize Low level rain-fed
reticulate::source_python("C:/LandPKS_API_SoilID-master/model/GAEZ_soilID_functions_lab-data.py")

SQI_dom_L <- list(list())
SQI_id_L <- list(list())
SQI_id_loc_L_epa <- list(list())
SQI_id_loc_L_val <- list(list())
SQI_id_loc_L_valv <- list(list())

for(i in 1:nrow(GH.profiles.val.df)){
  pedon_epa <- EPA_Soil_Data %>% dplyr::filter(Pedon_ID==GH.profiles.val.df$Pedon_ID[i])
  pedon_val <- Validation_Soil_Data %>% dplyr::filter(Pedon_ID==GH.profiles.val.df$Pedon_ID[i])
  SQI_dom_L[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$Dom_compID, CROP_ID='4', inputLevel='L', depthWt_type=1)
  SQI_id_L[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='4', inputLevel='L', depthWt_type=1)
  SQI_id_loc_L_epa[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='4', inputLevel='L', depthWt_type=1, plot_data=pedon_epa, site_data=pedon_epa)
  SQI_id_loc_L_val[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='4', inputLevel='L', depthWt_type=1, plot_data=pedon_val, site_data=pedon_val)
  SQI_id_loc_L_val_lab[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='4', inputLevel='L', depthWt_type=1, plot_data=pedon_val, site_data=pedon_val, lab_data=pedon_val)
}

# SQI_id_loc_L <- list(list())
# for(i in 1:nrow(GH.profiles.val.df)){
#   pedon <- LPKS_soil_profile_gh %>% dplyr::filter(id==GH.profiles.val.df$Pedon_ID[i])
#   SQI_id_loc_L[[i]] <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$SoilID_compID, CROP_ID='4', inputLevel='L', depthWt_type=1, plot_data=pedon)
# }

SQI_dom_L_df <-  bind_rows(SQI_dom_L)
SQI_dom_L_df <-  SQI_dom_L_df %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_dom=SQ1, SQ2_dom=SQ2, SQ3_dom=SQ3, SQ4_dom=SQ4, SQ5_dom=SQ5, SQ6_dom=SQ6, SQ7_dom=SQ7, SR_dom=SR, Input_Level = `Input Level`, SoilTax_dom=`Soil Tax`)

SQI_id_L_df <-  bind_rows(SQI_id_L)
SQI_id_L_df <-  SQI_id_L_df %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id=SQ1, SQ2_id=SQ2, SQ3_id=SQ3, SQ4_id=SQ4, SQ5_id=SQ5, SQ6_id=SQ6, SQ7_id=SQ7, SR_id=SR, Input_Level = `Input Level`, SoilTax_id=`Soil Tax`)

SQI_id_loc_L_df_epa <-  bind_rows(SQI_id_loc_L_epa)
SQI_id_loc_L_df_epa <-  SQI_id_loc_L_df_epa %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id_loc_epa=SQ1, SQ2_id_loc_epa=SQ2, SQ3_id_loc_epa=SQ3, SQ4_id_loc_epa=SQ4, SQ5_id_loc_epa=SQ5, SQ6_id_loc_epa=SQ6, SQ7_id_loc_epa=SQ7, SR_id_loc_epa=SR, Input_Level = `Input Level`, SoilTax_id_loc_epa=`Soil Tax`)

SQI_id_loc_L_df_val <-  bind_rows(SQI_id_loc_L_val)
SQI_id_loc_L_df_val <-  SQI_id_loc_L_df_val %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id_loc=SQ1, SQ2_id_loc=SQ2, SQ3_id_loc=SQ3, SQ4_id_loc=SQ4, SQ5_id_loc=SQ5, SQ6_id_loc=SQ6, SQ7_id_loc=SQ7, SR_id_loc=SR, Input_Level = `Input Level`, SoilTax_id_loc=`Soil Tax`)

SQI_id_loc_L_df_val_lab <-  bind_rows(SQI_id_loc_L_val_lab)
SQI_id_loc_L_df_val_lab <-  SQI_id_loc_L_df_val_lab %>% dplyr::mutate(PedonID = GH.profiles.val.df$Pedon_ID) %>% dplyr::select(PedonID, SQ1_id_loc_lab=SQ1, SQ2_id_loc_lab=SQ2, SQ3_id_loc_lab=SQ3, SQ4_id_loc_lab=SQ4, SQ5_id_loc_lab=SQ5, SQ6_id_loc_lab=SQ6, SQ7_id_loc_lab=SQ7, SR_id_loc_lab=SR, Input_Level = `Input Level`, SoilTax_id_loc_lab=`Soil Tax`)

LandPKS_SQI_L <- SQI_dom_L_df %>% full_join(SQI_id_loc_L_df_epa, by=c('PedonID', 'Input_Level')) %>% full_join(SQI_id_loc_L_df_val, by=c('PedonID', 'Input_Level')) %>% full_join(SQI_id_loc_L_df_val_lab, by=c('PedonID', 'Input_Level')) %>% dplyr::select(PedonID,Input_Level, SoilTax_dom, SoilTax_id_loc_epa, SoilTax_id_loc, SoilTax_id_loc_lab, SQ1_dom, SQ1_id_loc_epa, SQ1_id_loc, SQ1_id_loc_lab, SQ2_dom, SQ2_id_loc_epa, SQ2_id_loc, SQ2_id_loc_lab, SQ3_dom, SQ3_id_loc_epa, SQ3_id_loc, SQ3_id_loc_lab, SQ4_dom, SQ4_id_loc_epa, SQ4_id_loc, SQ4_id_loc_lab, SQ5_dom, SQ5_id_loc_epa, SQ5_id_loc, SQ5_id_loc_lab, SQ6_dom, SQ6_id_loc_epa, SQ6_id_loc, SQ6_id_loc_lab, SQ7_dom, SQ7_id_loc_epa, SQ7_id_loc, SQ7_id_loc_lab, SR_dom, SR_id_loc_epa, SR_id_loc, SR_id_loc_lab)


Ghana_aez <- LandPKS_SQI_L %>% dplyr::select(id=PedonID, Input_Level, SR_dom, SR_id_loc_epa, SR_id_loc, SR_id_loc_lab) %>% pivot_longer(cols=SR_dom:SR_id_loc_lab, names_to = 'source', values_to='SR')


Ghana_aez$source <- factor(Ghana_aez$source, levels = c('SR_dom', 'SR_id_loc_epa', 'SR_id_loc', 'SR_id_loc_lab'))

Ghana_aez %>% dplyr::group_by(source) %>% dplyr::summarize(mean(SR, na.rm=T), sd(SR, na.rm=T))
Ghana_aez_sub <- Ghana_aez %>% dplyr::filter(!source=='SR_id')

Ghana_aez_sub <- Ghana_aez_sub %>% rowwise() %>% dplyr::mutate(SC = S_Class(SR))
Ghana_aez_sub$SC <- factor(Ghana_aez_sub$SC, order = TRUE, levels =  c( "S0", "S1", "S2", "S3", "S4", "N"))


# Draw the basic boxplot
pdf(here("results/figures/Ghana_AEZ_boxplot_maize.pdf"), width = 6.5, height = 4.5)
a <- boxplot(Ghana_aez$SR ~ Ghana_aez$source , ylim=c(0,100), ylab="Soil Suitability" , xlab="Data Source" ,main="Maize Soil Suitability")


col_bl <- c("#4575b4","#91bfdb", "#e0f3f8", "#fee090", "#fc8d59", "#d73027")
agg <- count(Ghana_aez_sub %>% dplyr::group_by(source), SC)  
pdf(here("results/figures/Ghana_AEZ_barplot_maize.pdf"), width = 6.5, height = 4.5)
  p1 <- ggplot(agg) +
      geom_col(aes(x = source, y = n, fill = SC)) +
      scale_fill_manual(values = col_bl)
  p1
dev.off() 
```






```{r}
prof <- GAEZ_SQI(COMPID=GH.profiles.val.df[i,]$Dom_compID, CROP_ID='4', inputLevel='L', depthWt_type=1)

prof$CECc*(prof$CLPC/100) + (300*(prof$ORGC*.001))

CECs <- (prof$CECS - (250*(prof$ORGC*.001)))/(prof$CLPC/100)

```



# Pedotransfer calculation of reference bulk density (Saxton et al. [1986])
## Reference bulk density
Porosity @ sat (SAT) = =0.332-0.0007251*Sand+0.1276*LOG10(Clay)
Db = (1-SAT) * 2.65

# Pedotransfer calculation of actual bulk density (Saxton and Rawls [2006])
## Bulk density accounting for texture, OM, and gravel

1st Field Capacity step (%v) = Ɵ33t = 	-0.251 * (SAND) + 0.195 * (CLAY) + 0.011 * (OM) + 
					0.006 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) +
					0.452 * (SAND) * (CLAY) + 0.299

Field Capacity solution (%v) = Ɵ33 =	Ɵ33t + (1.283 * Ɵ33t * Ɵ33t - 0.374 * Ɵ33t - 0.015)

1st Saturated Field Capacity step (%v) = Ɵ(S-33)t = 0.278 * (SAND) + 0.034 * (CLAY) + 0.022 * (OM) – 
				0.018 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) – 
				0.584 * (SAND) * (CLAY) + 0.078

Saturated Field Capacity Solution (%v) = Ɵ(S-33) = Ɵ(S-33)t + ( ( 0.636 * Ɵ(S-33)t ) – 0.107 )

Sand Adjustment Saturated Conductivity = Ɵs = Ɵ33 + Ɵ(S-33) – 0.097 * (SAND) + 0.043

Matric soil density w/ OM  = (ρN)	= ( 1-  Ɵs ) * 2.65

Bulk soil density w/ gravel = (ρB) = ( 1 - ( GC ) ) / ( 1 - ( GC ) *( 1 - 1.5 * ( ρN /2.65) ) )

```{r}
#Function to calculate ref bulk density (based on Saxton et al. 1986)
act_bulk <- function(SAND, OM, CLAY, RFV){
  fc1 <- -0.251 * (SAND) + 0.195 * (CLAY) + 0.011 * (OM) + 0.006 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) + 0.452 * (SAND) * (CLAY) + 0.299
  fc <- fc1 + (1.283 * fc1^2 - 0.374 * fc1 - 0.015)
  sfc1 <- 0.278 * (SAND) + 0.034 * (CLAY) + 0.022 * (OM) - 0.018 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) - 0.584 * (SAND) * (CLAY) + 0.078
  sfc <- sfc1 + ((0.636 * sfc1) - 0.107)
  sasc <- fc + sfc - 0.097 * (SAND) + 0.043
  md <- ( 1 - sasc ) * 2.65
  Db <- md*( 1 - RFV) + (RFV * 2.65)
  return(Db)
}
act_bulk(.80, .1, .15, .50)



SAND = .82
OM = 1
CLAY= .06
RFV = .25


#revised code
fc1 <- -0.251 * (SAND) + 0.195 * (CLAY) + 0.011 * (OM) + 0.006 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) + 0.452 * (SAND) * (CLAY) + 0.299
fc <- fc1 + (1.283 * fc1^2 - 0.374 * fc1 - 0.015)
sfc1 <- 0.278 * (SAND) + 0.034 * (CLAY) + 0.022 * (OM) - 0.018 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) - 0.584 * (SAND) * (CLAY) + 0.078
sfc <- sfc1 + ((0.636 * sfc1) - 0.107)
sasc <- fc + sfc - 0.097 * (SAND) + 0.043
md <- ( 1 - sasc ) * 2.65
Db <- md*( 1 - RFV) + (RFV * 2.65)
fifteen_t <- -0.024 * (SAND) + 0.487 * (CLAY) + 0.006 * (OM) + 0.005 * (SAND) * (OM) - 0.013 * (CLAY) * (OM) + 0.068 * (SAND) * (CLAY) + 0.031
fifteen <- fifteen_t + (0.14 * fifteen_t - 0.02)
lambda = (log(fc)- log(fifteen))/ (log(1500) - log(33))
RFw = RFV / ( (md / 2.65 ) + RFV * ( 1 - (md / 2.65 ) ) )
KbKs   =     ( 1 -  RFw  ) / ( 1 - RFw  *( 1 - 1.5 * (md / 2.65) ) )


inf1 <- 1930 * (sasc - fc)^(3- lambda) * KbKs
awc1 <- (fc - fifteen) * (1 - (RFV)) * 20


#old code
fc1 <- -0.251 * (SAND) + 0.195 * (CLAY) + 0.011 * (OM) + 0.006 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) + 0.452 * (SAND) * (CLAY) + 0.299
fc <- fc1 + (1.283 * fc1^2 - 0.374 * fc1 - 0.015)
fc_scale = fc*100
sfc1 <- 0.278 * (SAND) + 0.034 * (CLAY) + 0.022 * (OM) - 0.018 * (SAND) * (OM) - 0.027 * (CLAY) * (OM) - 0.584 * (SAND) * (CLAY) + 0.078
sfc <- sfc1 + ((0.636 * sfc1) - 0.107)
sasc <- fc + sfc - 0.097 * (SAND) + 0.043
md <- ( 1 - sasc ) * 2.65

gravels_AB = ((md/2.65)*RFV)/(1-RFV*(1-md/2.65))


Db <- md*( 1 - gravels_AB) + (gravels_AB * 2.65)
fifteen_t <- -0.024 * (SAND) + 0.487 * (CLAY) + 0.006 * (OM) + 0.005 * (SAND) * (OM) - 0.013 * (CLAY) * (OM) + 0.068 * (SAND) * (CLAY) + 0.031
fifteen <- fifteen_t + (0.14 * fifteen_t - 0.02)
fifteen_scale <- fifteen *100
lambda = abs(log(fifteen)- log(fc))/ (log(1500) - log(33))
#RFw = RFV / ( (md / 2.65 ) + RFV * ( 1 - (md / 2.65 ) ) )
bds   =     ( 1 -  RFV  ) / ( 1 - RFV  *( 1 - 1.5 * (md / 2.65) ) )
poc = (1 - (md/2.65))

inf2 <- 1930 * (sasc - fc)^(3- lambda) * bds
awc2 <- (fc - fifteen) * (1 - (gravels_AB)) * 20




Loamy Sand







```

# Code to calculate the modified Fournier Index
```{r}
dtm_slope_merit.dem_m_250m_s0..0cm_2017_v1.0.tif

in.tif.lst ="/vsicurl/https://s3.eu-central-1.wasabisys.com/africa-soil/layers30m/dtm_slope_aw3d30.nasadem_m_30m_s0..0cm_2017_africa_proj.laea_v0.1.tif"


in.tif.lst ="/vsicurl/https://s3.eu-central-1.wasabisys.com/openlandmap/layers250m/dtm_slope_merit.dem_m_250m_s0..0cm_2017_v1.0.tif"
library(terra)

in.tif.lst = paste0("/vsicurl/https://s3.eu-central-1.wasabisys.com/openlandmap/layers1km/",
      "clm_precipitation_sm2rain.", c("jan", "feb", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec"), 
      "_m_1km_s0..0cm_2007..2018_v0.2.tif")
xy.lst = data.frame(lon=c(4.057, 11.360, 17.911, 10.208, 16.273, -3.799, -1.148, -8.180, 20.833, 16.676),
           lat=c(50.3871, 61.962, 47.252, 46.276, 40.605, 38.335, 52.572, 53.591, 42.077, 51.347))
ov = parallel::mclapply(in.tif.lst, function(i){terra::extract(rast(i), xy.lst)}, mc.cores = 10)


xy = data.frame(lon=-3.799, lat=38.335)

ov = lapply(in.tif.lst, function(i){terra::extract(rast(i), xy.lst)})
t(bind_cols(ov))

# mfi = sum(monthly prec^2)/Annual P
mfi <- function(data){
  
  
  
  
}
```

